Story Cloze Task: UW NLP System

### 2017-02-16 docs/shared_task_paper_camera_ready.tex
Camera ready style changes 2

\section*{Acknowledgments}
The authors thank the shared task organizers and anonymous reviewers
for feedback.  \nascomment{anyone else} This research was supported in
part by the Allen Institute for Artificial Intelligence and in part by
DARPA under the Communicating with Computers program.

>>>>

\section*{Acknowledgments}
The authors thank the shared task organizers and anonymous reviewers
for feedback.\resolved{\nascomment{ anyone else}} This research was supported in
part by the Allen Institute for Artificial Intelligence and in part by
DARPA under the Communicating with Computers program.
